RVD2: An ultra-sensitive variant detection model for low-depth targeted next-generation sequencing data

### 2013-11-26 doc/bioinformatics2013/RVD2.tex
added rs positions to HCC calls.

RVD2 identified 5 variants in the 44,716bp PAXIP1 gene. Of the five called variants, three were homozygous germline variants and two were heterozygous germline variants. The two heterozygous variants had a loss-of-heterozygosity in the tumor sample. None of the identified mutations are at known dnSNPX.X locations.

Figure~\ref{fig:brca_MAF} shows the estimated minor allele frequencies for the normal and tumor samples at the called locations. Positions chr7:743899XC$>$T, chr7:753635T$>$C and chr7:780960C$>$T are germline homozygous mutations. Positions chr7:754371 and chr7:758813 are called heterozygous in the normal sample. In the tumor cells we identified all five mutations chr7:743899C$>$T, chr7:753635T$>$C, chr7:754371T$>$C, chr7:758813G$>$A, and chr7:780960C$>$T. Positions chr7:754371T$>$C and chr7:758813G$>$A are identified as loss-of-heterozygosity events.

% TODO: replace X>X with the reference and mutated base here
% Done

@@

The original research describing this sample used Strelka to identify mutations in the same sample. They identified chr7:154760439 as variant, but missed the other four variants.

>>>>

RVD2 identified five variants in the 44kbp PAXIP1 gene from chr7:XXX to chr7:XXX. Of the five called variants, three were homozygous germline variants and two were heterozygous germline variants. The two heterozygous variants had a loss-of-heterozygosity in the tumor sample.

Figure~\ref{fig:brca_MAF} shows the estimated minor allele frequencies for the normal and tumor samples at the called locations. Positions chr7:154743899C$>$T, chr7:154753635T$>$C and chr7:154780960C$>$T are germline homozygous mutations. Positions chr7:154754371 and chr7:154758813 are called heterozygous in the normal sample. In the tumor cells we identified all five mutations chr7:154743899C$>$T, chr7:154753635T$>$C, chr7:154754371T$>$C, chr7:154758813G$>$A, and chr7:154780960C$>$T. Positions chr7:154754371T$>$C and chr7:154758813G$>$A then loss-of-heterozygosity events.

%According to dbSNPv138 chr7:154743899 is rs1239326, chr7:154753635 is rs1239324, chr7:154754371 is rs71534174, chr7:154758813 is rs35505514, and chr7:154780960 is rs4398858.
%TODO: place these rs labels beneath the position labels on the x-axis of the figure. Remove the above sentence and add. 
%Some of these mutations are also found to be common population SNPs according to dbSNPv138. The corresponding rs identities are shown in the figure.

@@

The original research describing this sample used Strelka to identify mutations in the same sample. They identified chr7:154760439 as variant, but did not call the other four variants. In particular strelka missed the two LOH events.
